Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-11 manuscript.tex
figure pathways

\note{get the rights or redo a schematics}
\includegraphics[width=.7\textwidth]{figures/visual-latency-estimate.jpg}
\caption{From~\citep{thorpe_seeking_2001} }\label{fig:thorpe}

>>>>

\includegraphics[width=.7\textwidth]{figures/visual-latency.pdf}
% thorpe
% \includegraphics[width=.7\textwidth]{figures/visual-latency-estimate.jpg}%-estimate.jpg}
\caption{Latency of the different processing steps along the visual pathway in order of activation from a visual stimulus. Different areas are schematically represented by ellipses, along with their activation latency. In order, Retina, $20-40~\ms$; V1, $40-60~\ms$; IT, $80-100~\ms$; MC, $140-190~\ms$; to finger mescles, $180-260~\ms$.Figured inspired by a similar schematics done for monkeys in~\citep{thorpe_seeking_2001}. The latencies in macaque monkey are about: Retina, $20-40~\ms$; V1, $40-60~\ms$; IT, $80-100~\ms$; MC, $140-190~\ms$; to finger mescles, $180-260~\ms$.}\label{fig:thorpe}
